\begin{abstract}

% background
Animated infographics are a potent storytelling tool in various fields, from business to science communication. However, their creation is often laborious, involving meticulous element selection, property adjustments, and timing management.
% Gaia
Therefore, we propose \gaia{}, a declarative grammar designed to streamline animated infographic creation.
With \gaia{}, users can craft animations expressively and intuitively, abstracting away the underlying implementation.
Via an abstraction of animated targets, \gaia{} provides an approach to express, save and share infographic animations from expert designers and allows novices to reuse them, significantly speeding up the creation process.
% Evaluation
We implemented a componentized \gaia{} compiler prototype and built a demo system based on it with diverse examples to showcase its usability.
In a user study involving non-expert participants, individuals with no prior animation experience successfully replicated real-world animations within just one hour of learning.
\gaia{} has been applied in several practical projects, further advancing the field of animated infographic authoring.

% Animated infographics are a potent storytelling tool in various fields, from business to science communication. However, their creation is often laborious, involving meticulous element selection, property adjustments, and timing management. 
% Therefore, we propose Gaia, a declarative grammar designed to streamline animated infographic creation. With Gaia, users can craft animations expressively and intuitively, abstracting away the underlying implementation. Via an abstraction of animated targets, Gaia provides an approach to express, save and share infographic animations from expert designers and allows novices to reuse them, significantly speeding up the creation process. 
% We implemented a componentized Gaia compiler prototype and built a demo system based on it with diverse examples to showcase its usability. In a user study involving non-expert participants, individuals with no prior animation experience successfully replicated real-world animations within just one hour of learning. Gaia has been applied in several practical projects, further advancing the field of animated infographic authoring.

\end{abstract}